Evaluation of performances

### 2021-03-29 analysis/eval-performance.Rmd
wflow_publish(knitr_in("analysis/eval-performance.Rmd"), view = FALSE,     verbose = TRUE)

- Fold 1: Luiando
- Fold 2: Laukiz1
- Fold 3: Laukiz2
- Fold 4: Oiartzun

```{r}
df <- mlr::getBMRPerformances(bm_aggregated,
  "hr", "SVM MBO No Filter",
  as.df = TRUE
)
df_tab <- df %>%
  dplyr::select(iter, rmse) %>%
  dplyr::rename(Plot = iter, RMSE = rmse) %>%
  dplyr::mutate(`Test Plot` = as.character(Plot)) %>%
  dplyr::mutate(`Test Plot` = forcats::fct_recode(`Test Plot`,
    Laukiz1 = "2", Laukiz2 = "3",
    Luiando = "1", Oiartzun = "4"
  )) %>%
  dplyr::mutate(RMSE = round(RMSE, 2))

@@

df_tbl <- getBMRTuneResults(bmr_inspect_tune, as.df = TRUE) %>%
  dplyr::rename(Learner = learner.id) %>%
  dplyr::rename(Plot = iter) %>%
  dplyr::rename(RMSE = rmse.test.mean) %>%
  dplyr::rename("Features (\\%)" = fw.perc) %>%
  dplyr::mutate(`Test Plot` = as.character(Plot)) %>%
  dplyr::mutate(`Test Plot` = forcats::fct_recode(`Test Plot`,
    Oiartzun = "2", Luiando = "3",
    Laukiz1 = "1", Laukiz2 = "4"
  )) %>%
  dplyr::mutate(Learner = forcats::fct_recode(Learner,
    "RF \\\\ Car" = "RF MBO Car", "XGB \\\\ Borda" = "XGBOOST MBO Borda",
    "SVM \\\\ Relief" = "SVM MBO Relief"
  )) %>%
  dplyr::mutate(Learner = as.character(Learner)) %>%
  dplyr::mutate(`Test Plot` = as.character(`Test Plot`)) %>%
  dplyr::mutate("\\#" = case_when(
    `Test Plot` == "Laukiz1" ~ ceiling(`Features (\\%)` * 559),
    `Test Plot` == "Laukiz2" ~ ceiling(`Features (\\%)` * 451),
    `Test Plot` == "Luiando" ~ ceiling(`Features (\\%)` * 301),
    `Test Plot` == "Oiartzun" ~ ceiling(`Features (\\%)` * 497),
  )) %>% 
  dplyr::group_by(Learner) %>%
  dplyr::select(Learner, `Test Plot`, "Features (\\%)", "\\#", RMSE)

>>>>

- Fold 1: Laukiz1
- Fold 2: Laukiz2
- Fold 3: Luiando
- Fold 4: Oiartzun

```{r}
df <- mlr::getBMRPerformances(bm_aggregated,
  "hr", "SVM MBO No Filter",
  as.df = TRUE
)
df_tab <- df %>%
  dplyr::select(iter, rmse) %>%
  dplyr::rename(Plot = iter, RMSE = rmse) %>%
  dplyr::mutate(`Test Plot` = as.character(Plot)) %>%
  dplyr::mutate(`Test Plot` = forcats::fct_recode(`Test Plot`,
    Laukiz1 = "1", Laukiz2 = "2",
    Luiando = "3", Oiartzun = "4"
  )) %>%
  dplyr::mutate(RMSE = round(RMSE, 2))

@@

df_tbl <- getBMRTuneResults(bmr_inspect_tune, as.df = TRUE) %>%
  dplyr::rename(Learner = learner.id) %>%
  dplyr::rename(Plot = iter) %>%
  dplyr::rename(RMSE = rmse.test.mean) %>%
  dplyr::rename("Features (\\%)" = fw.perc) %>%
  dplyr::mutate(`Test Plot` = as.character(Plot)) %>%
  dplyr::mutate(`Test Plot` = forcats::fct_recode(`Test Plot`,
    Oiartzun = "4", Luiando = "3",
    Laukiz1 = "1", Laukiz2 = "2"
  )) %>%
  dplyr::mutate(Learner = forcats::fct_recode(Learner,
    "RF \\\\ Car" = "RF MBO Car", "XGB \\\\ Borda" = "XGBOOST MBO Borda",
    "SVM \\\\ Relief" = "SVM MBO Relief"
  )) %>%
  dplyr::mutate(Learner = as.character(Learner)) %>%
  dplyr::mutate(`Test Plot` = as.character(`Test Plot`)) %>%
  dplyr::mutate("\\#" = case_when(
    `Test Plot` == "Laukiz1" ~ ceiling(`Features (\\%)` * 479),
    `Test Plot` == "Laukiz2" ~ ceiling(`Features (\\%)` * 451),
    `Test Plot` == "Luiando" ~ ceiling(`Features (\\%)` * 300),
    `Test Plot` == "Oiartzun" ~ ceiling(`Features (\\%)` * 529),
  )) %>% 
  dplyr::group_by(Learner) %>%
  dplyr::select(Learner, `Test Plot`, "Features (\\%)", "\\#", RMSE)
